Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-08-12 analysis/Study1.qmd
added data + updated dimensions/columns across samples

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
    MAIA_AttentionRegulation = MAIA_AttentionReg, MAIA_BodyListening = MAIA_BodyListening,
    MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
    MAIA_NotDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
rm(data)
```

@@

```{r}
df3 <- haven::read_sav("../data/Campos2022/Dataset_Test.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
  )
```

@@

- Todd (2022) 
  - https://osf.io/ms354/
  - MAIA does not include items for not-worrying and not-distracting

@@

df4$MAIA_AttentionReg <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
df4$MAIA_EmoAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
df4$MAIA_SelfReg<- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
df4$MAIA_Noticing <- rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)
```

@@

```{r}
df6 <- haven::read_sav("../data/Brand2022/LatentVariableApproach.sav") |> 
  select(-SERIAL) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )
```

@@

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = MAIA_NOTICING, MAIA_NotDistracting = MAIA_NON_DISTRACTING,
    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionReg = mAIA_ATTENTION_REGULATION,
    MAIA_SelfReg = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) x - 1)) # Original scale 1-6

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = maiaNotice, MAIA_NotDistracting = maiaNonDistracting,
    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionReg = maiaAttentionRegulation,
    MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5)))) # Original scale 1-5

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
    ICQ = ICQ_sum
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
```

@@

df8b <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
  rename(
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH)
```

@@

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )
```

@@

```{r}
df11  <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    typeSample = Sample
  ) |>
  mutate(
    MAIA2_NotDistracting_1_R = 1 - MAIA2_NotDistracting_1_R,
    MAIA2_NotDistracting_2_R = 1 - MAIA2_NotDistracting_2_R,
    MAIA2_NotDistracting_3_R = 1 - MAIA2_NotDistracting_3_R,
    MAIA2_NotDistracting_4_R = 1 - MAIA2_NotDistracting_4_R,
    MAIA2_NotDistracting_5_R = 1 - MAIA2_NotDistracting_5_R,
    MAIA2_NotDistracting_6_R = 1 - MAIA2_NotDistracting_6_R,
    MAIA2_NotWorrying_1_R = 1 - MAIA2_NotWorrying_1_R,
    MAIA2_NotWorrying_2_R = 1 - MAIA2_NotWorrying_2_R,
    MAIA2_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R) |> 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))

@@

# Compute subscales
df13$MAIA_AttentionReg <- rowMeans(select(df13 , starts_with("MAIA_Attention")))
df13$MAIA_EmoAwareness <- rowMeans(select(df13 , starts_with("MAIA_Emotional")))
df13$MAIA_Noticing <- rowMeans(select(df13 , starts_with("MAIA_Noticing")))
df13$MAIA_BodyListening <- rowMeans(select(df13 , starts_with("MAIA_BodyListening")))
df13$MAIA_NotDistracting<- rowMeans(select(df13 , starts_with("MAIA_NotDistracting")))
df13$MAIA_NotWorrying<- rowMeans(select(df13 , starts_with("MAIA_NotWorrying")))
df13$MAIA_SelfReg<- rowMeans(select(df13 , starts_with("MAIA_SelfRegulation")))
df13$MAIA_Trusting<- rowMeans(select(df13 , starts_with("MAIA_Trusting")))
```

@@

```{r}
df14  <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |> #anx_21 , tas20_21 are attention checks
  mutate_all(as.numeric) |>
  rename(
    Age = AGE, Gender = GENDER,
    Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4,
    Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7, Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9,
    Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
    Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22,
    MAIA_EmoAwareness =MAIA_Emotional, MAIA_SelfReg = MAIA_SelfRegulation, MAIA_AttentionReg = MAIA_Attention
  ) |>
   mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 5) ~ "Other",
    Gender == 4 ~ "NA"
  )) |> ## compute dimensions for the TAS
  mutate(TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
         TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
         TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20) 
```

@@

>>>>

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
    MAIA_Trusting = MAIA_BodyTrusting,
    BPQ_BodyAwareness = BPQ_A, BPQ_AutonomicReactivity = BPQ_R)
rm(data)
```

@@

```{r}
df3 <- haven::read_sav("../data/Campos2022/Dataset_Test.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21,
    TAS_EOT = TAS_ExternallyOrientedThinking, TAS_DIF = TAS_IdentifyingFeelings, TAS_DDF = TAS_DescribingFeelings
  )
```

@@

- Todd (2022) 
  - https://osf.io/ms354/
  - MAIA does not include items for not-worrying and not-distracting 
  - BPQ 26 - body awareness

@@

df4$MAIA_AttentionReg <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
df4$MAIA_EmoAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
df4$MAIA_SelfReg<- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
df4$MAIA_Noticing <- rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)

df4$BPQ_BodyAwareness <- rowMeans(select(df4, starts_with("BPQ")), na.rm = TRUE)
```

@@

```{r}
df6 <- haven::read_sav("../data/Brand2022/LatentVariableApproach.sav") |> 
  select(-SERIAL) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    PHQ2_Sum= PHQ2_sum,
    GAD2_Sum = GAD2_sum
  )
```

@@

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = MAIA_NOTICING, MAIA_NotDistracting = MAIA_NON_DISTRACTING,
    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionReg = mAIA_ATTENTION_REGULATION,
    MAIA_SelfReg = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS,
    STAIT_Sum = STAI_T_Sumscore
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) x - 1)) # Original scale 1-6

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = maiaNotice, MAIA_NotDistracting = maiaNonDistracting,
    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionReg = maiaAttentionRegulation,
    MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness,
    BPQ_BodyAwareness =BPQ_Sum

  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5)))) # Original scale 1-5

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
    ICQ = ICQ_sum,
    STAIT_Sum = STAIT_sum
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
```

@@

df8a$BPQ_BodyAwareness <- rowMeans(select(df8a, starts_with("BPQ")), na.rm = TRUE)

df8b <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
  rename(
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH,
    PHQ15_Sum = PHQ15_sum,
    PHQ9_Sum = PHQ9_sum)
```

@@

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |>
  mutate(
    BFI_NEUROTICISM = (BFI_1 + BFI_2 + BFI_3)/3,
    BFI_AGREEABLENESS = (BFI_10R + BFI_11 + BFI_12)/3,
    BFI_EXTROVERSION = (BFI_4 + BFI_5 + BFI_6),
    BFI_CONSCIENTIOUSNESS = (BFI_13 + BFI_14 + BFI_15R)/3,
    BFI_OPENNESS = (BFI_7 + BFI_8 + BFI_9)/3
    )
```

@@

```{r}
df11  <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    typeSample = Sample,
    STAIT_Sum = STAI5_General,
    BDI_Sum = BDI2_Total
  ) |>
  mutate(
    MAIA2_NotDistracting_1_R = 1 - MAIA2_NotDistracting_1_R,
    MAIA2_NotDistracting_2_R = 1 - MAIA2_NotDistracting_2_R,
    MAIA2_NotDistracting_3_R = 1 - MAIA2_NotDistracting_3_R,
    MAIA2_NotDistracting_4_R = 1 - MAIA2_NotDistracting_4_R,
    MAIA2_NotDistracting_5_R = 1 - MAIA2_NotDistracting_5_R,
    MAIA2_NotDistracting_6_R = 1 - MAIA2_NotDistracting_6_R,
    MAIA2_NotWorrying_1_R = 1 - MAIA2_NotWorrying_1_R,
    MAIA2_NotWorrying_2_R = 1 - MAIA2_NotWorrying_2_R,
    MAIA2_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R) |> 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))

@@

# Compute subscales
df13$MAIA_AttentionReg <- rowMeans(select(df13 , starts_with("MAIA_Attention")))
df13$MAIA_EmoAwareness <- rowMeans(select(df13 , starts_with("MAIA_Emotional")))
df13$MAIA_Noticing <- rowMeans(select(df13 , starts_with("MAIA_Noticing")))
df13$MAIA_BodyListening <- rowMeans(select(df13 , starts_with("MAIA_BodyListening")))
df13$MAIA_NotDistracting<- rowMeans(select(df13 , starts_with("MAIA_NotDistracting")))
df13$MAIA_NotWorrying<- rowMeans(select(df13 , starts_with("MAIA_NotWorrying")))
df13$MAIA_SelfReg<- rowMeans(select(df13 , starts_with("MAIA_SelfRegulation")))
df13$MAIA_Trusting<- rowMeans(select(df13 , starts_with("MAIA_Trusting")))

df13$PHQ4_Depression <- (df13$PHQ4_Depression_4 + df13$PHQ4_Depression_3)/2
df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2
```

@@

```{r}
df14  <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |> #anx_21 , tas20_21 are attention checks
  mutate_all(as.numeric) |>
  rename(
    Age = AGE, Gender = GENDER,
    Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4,
    Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7, Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9,
    Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
    Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22,
    MAIA_EmoAwareness =MAIA_Emotional, MAIA_SelfReg = MAIA_SelfRegulation, MAIA_AttentionReg = MAIA_Attention,
    STAIT_Sum = ANX
  ) |>
   mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 5) ~ "Other",
    Gender == 4 ~ "NA"),
    TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
    TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
    TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20) 
```

@@

### Sample 16

- Raquel Arjona and Robyn Scharte data

df16 <- read.csv("../data/Scharte2025/data_IAS_rs.csv") |>
  rename(Age= age, Gender = gender_identity,
         Heart = ias1, Hungry = ias2, Breathing = ias3, Thirsty = ias4, Urinate = ias5, 
         Defecate=ias6, Taste = ias7,Vomit = ias8, Sneeze = ias9, Cough = ias10, 
         Temp = ias11, Sex_arousal = ias12, Wind = ias13, Burp = ias14,Muscles = ias15, 
         Bruise = ias16, Pain = ias17, Blood_Sugar = ias18, Affective_touch = ias19, 
         Tickle =ias20, Itch = ias21,
         ) |>
  mutate(Gender = case_when(
    Gender == "1" ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 4, 5) ~ "Other",
    Gender == 6 ~ "NA"),
    MAIA_Noticing = (maia1 + maia2 + maia3 + maia4)/4,
    MAIA_NotDistracting = (maia5_rev + maia6_rev + maia7_rev +maia8_rev + maia9_rev + maia10_rev)/6, 
    MAIA_NotWorrying = (maia11_rev +maia12_rev  + maia13)/3,
    MAIA_AttentionReg = (maia16 + maia17 + maia18 + maia19 + maia20 + maia21 + maia22)/7,
    MAIA_EmoAwareness = (maia23 + maia24 + maia25 + maia26 +maia27)/5,
    MAIA_SelfReg = (maia28 + maia29 + maia30 + maia31)/4,
    MAIA_BodyListening = (maia32 + maia33 +maia34)/3,
    MAIA_Trusting = (maia35 + maia36 + maia37)/3 ,
    GAD7_Sum = rowSums(across(starts_with("gad1_")), na.rm = TRUE),
    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE))
